Examining the case behind Acer Platanoides' plight on Toronto's Street Trees 

### 2024-12-04 paper/paper.qmd
Updated title

---
title: "Examining the case behind Acer Platanoide's plight on Toronto's Street Trees "
subtitle: ""
author: 
  - Veyasan Ragulan
thanks: "Code and data are available at: https://github.com/Veyasan1/STA3014-Paper1"
date: today
date-format: long
abstract: "Acer platanoides is an invasive species that has taken over the streets of Toronto. Using the Street Tree data from OpenData Toronto, this paper examines the patterns and trends behind this spread. A linear model was created to predict species based on ward, street and cross streets. The model didn't find directionalyty to Acer platanoides' spread, suggested that volumes of Acer platanoides should be monitored instead."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Examining the case behind Acer Platanoides' plight on Toronto's Street Trees "
subtitle: ""
author: 
  - Veyasan Ragulan
thanks: "Code and data are available at: https://github.com/Veyasan1/STA3014-Paper1"
date: today
date-format: long
abstract: "Acer platanoides is an invasive species that has taken over the streets of Toronto. Using the Street Tree data from OpenData Toronto, this paper examines the patterns and trends behind this spread. A linear model was created to predict species based on ward, street and cross streets. The model didn't find directionalyty to Acer platanoides' spread, suggested that volumes of Acer platanoides should be monitored instead."
format: pdf
number-sections: true
bibliography: references.bib
---
